A Reproducible Data Analysis Workflow with RMarkdown, Git, Make & Docker

### 2019-11-12 manuscript.Rmd
typo fixes manuscript
fix three typos including wrong package name rodoc > redoc

Each tool in the workflow reduces the chances of non-reproducibility. Dynamic reporting with R Markdown guarantees consistency between computational results and their reporting; Version control with Git ensures permanence and consistency across multiple versions of data and code; Dependency management with Make affirms defined entry-points and dependency resolution; containerization with Docker secures reproducibility of the full computational environment. We believe that this tightening of loose ends does not restrict researchers but enables them to operate on a solid basis to deliver sound and sustainable research.

>>>>

Each tool in the workflow reduces the chances of non-reproducibility. Dynamic reporting with R Markdown guarantuees consistency between computational results and their reporting; Version control with Git ensures permanence and consistency across multiple versions of data and code; Dependency management with Make affirms defined entry-points and dependency resolution; containerization with Docker secures reproducibility of the full computational environment. We believe that this tightening of loose ends does not restrict researchers but enables them to operate on a solid basis to deliver sound and sustainable research.
